% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chen Zhiyang}



\basicInfo{
  \email{1792266893@qq.com} \textperiodcentered\ 
  \phone{(+86) 15588770792} \textperiodcentered\ 
  \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}
  
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2016 -- Present}
\textit{Bachelor student} in Software Engineering (EE), expected July 2020

\section{\faUsers\ Experience}

\subsection{\textbf{Selected Course Projects}}
\begin{itemize}
   \item \textbf{Model Search System based on VR image}：Course project of HCI，with members of 3.The project is developed using VRTK on Unity platform，and is based on the VR high school experiment project. Users can easily draw in the VR environment and will get the experiment tool they want. This project got a 98 score and ranks top in the whole class.
  \item \textbf{基于VR环境的折纸模拟系统}：游戏开发与设计课程大作业，三人团队项目。参考论文《》和项目，在Unity开发平台进行纸张的物理仿真引擎的搭建，并将其移植入VR环境，为使用者提供VR交互体验。该课程作业获得96分，在此课程中排名第二。

\end{itemize}

\datedsubsection{\textbf{Oxford University} Oxford, U.K.}{August 2018}
\role{Summer Exchange}{2 weeks}
Brief introduction: This is a bachelor exchange program of Shanghai Jiao Tong University called "Jing'e". I was chosen to be one of the 15 students, fully funded for a two-week exchange program.



\datedsubsection{\textbf{Scientific Research Experience}}{2018}
\role{Dalab of SJTU SE}{supervised by Professor Yang Xubo}
Current research program: Magic Toon
\begin{itemize}
  \item Implemented a dataset segmentation tool
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Python, Java, JavaScript
  \item Platform: Linux
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{National Encouragement Scholarship }{2017}
\datedline{C prize of Shanghai Jiao Tong University}{2017 2018}
\datedline{Honorable Mention in The Mathematics Contest in Modeling of Year 2018}{2018}
\datedline{Three Good Student of Shanghai Jiao Tong University}{2017 2018}
\datedline{Excellent League Member of Shanghai Jiao Tong University}{2017 2018}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/changeyoung98
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}


%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}

\end{document}





